---
title: "Causal inference is not just a statistics problem"
format: html
---

```{r}
#| label: setup
library(tidyverse)
library(quartets)
```

## Your turn 1

For each of the following 4 datasets, look at the correlation between `exposure` and `covariate`: 

* `causal_collider`
* `causal_confounding`
* `causal_mediator`
* `causal_m_bias`


```{r}
causal_quartet |> 
  group_by(dataset) |> 
  summarize(correlation = cor(exposure, covariate))
```

For each of the above 4 datasets, create a scatterplot looking at the relationship between `exposure` and `outcome`

```{r}
causal_quartet |> 
  ggplot(aes(exposure, outcome)) + 
  geom_point() + 
  geom_smooth(method = "lm", formula = "y ~ x") + 
  facet_wrap(~ dataset)
```

For each of the above 4 datasets, fit a linear model to examine the relationship between the `exposure` and the `outcome`

```{r}
causal_quartet |> 
    group_by(dataset) |> 
    summarize(exposure_coef = coef(lm(outcome ~ exposure))[["exposure"]])
```

## Your turn 2

For each of the following 4 datasets, fit a linear linear model examining the relationship between `outcome_followup` and `exposure_baseline` adjusting for `covariate_baseline`: 

* `causal_collider_time`
* `causal_confounding_time`
* `causal_mediator_time`
* `causal_m_bias_time`

```{r}
causal_quartet_time |> 
    group_by(dataset) |> 
    summarize(exposure_coef = coef(lm(outcome_followup ~ exposure_baseline + covariate_baseline))[["exposure_baseline"]])
```


