---
title: "Propensity Score Weighting"
format: html
---


```{r setup}
library(tidyverse)
library(broom)
library(touringplans)
library(propensity)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **exposure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

Below is the propensity score model you created in the previous exercise.

```{r}
#| eval: true
seven_dwarfs <- seven_dwarfs_train_2018 |>
  filter(hour == 9)

propensity_model <- glm(
  extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
  data = seven_dwarfs,
  family = binomial()
)

seven_dwarfs_prop <- propensity_model |>
  augment(type.predict = "response", data = seven_dwarfs)
```

## Your Turn 1 (Matching)

_After updating the code chunks below, change `eval = TRUE` before rendering._

Create at "matched" data set using the same propensity score model as above and a caliper of 0.2.

```{r}
#| eval: true
library(MatchIt)
matched_dwarfs <-  matchit(
  extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
  data = seven_dwarfs,
  link = "linear.logit",
  caliper = 0.2
)

matched_df <- get_matches(matched_dwarfs)
```

## Your Turn 2 (Weighting)

_After updating the code chunks below, change `eval = TRUE` before rendering._

Add the ATE weights to the data frame, `seven_dwarfs_prop`

```{r}
#| eval: true
seven_dwarfs_prop <- seven_dwarfs_prop |>
  mutate(w_ate = wt_ate(.fitted, extra_magic_morning))
```


Stretch Goal 1: 

Add ATM weights to the data frame, `seven_dwarfs_prop`

```{r}
#| eval: true
seven_dwarfs_prop <- seven_dwarfs_prop |>
  mutate(w_atm = wt_atm(.fitted, extra_magic_morning))
```

Stretch Goal 2: 

Update the code below to examine the distribution of the weighted sample. **HINT** the part that needs to be updated is the `weight` parameter in two of the `geom_mirror_histogram()` call.


```{r}
#| eval: true
#| warning: false
library(halfmoon)
ggplot(
  seven_dwarfs_prop, 
  aes(.fitted, fill = factor(extra_magic_morning))
) +
  geom_mirror_histogram(bins = 50, alpha = .5) +
  geom_mirror_histogram(aes(weight = w_ate), alpha = .5, bins = 50) +
  geom_hline(yintercept = 0, lwd = 0.5) +
  theme_minimal() +
  scale_y_continuous(labels = abs) +
  scale_fill_manual(values = c("blue", "green")) +
  labs(x = "p", fill = "Extra Magic Morning") +
  xlim(0, 1) 
```
