---
title: "Propensity Score Diagnostics"
output: html_document
---


```{r}
library(tidyverse)
library(broom)
library(tidysmd)
library(touringplans)
library(ggecdf)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **expsoure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

Below is the propensity score model and weights you created in the previous exercise.

```{r, eval = FALSE}
seven_dwarfs <- seven_dwarfs_train_2018 %>%
  filter(hour == 9)

propensity_model <- glm(
  extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
  data = seven_dwarfs,
  family = binomial()
)

df <- propensity_model %>%
  augment(type.predict = "response", data = seven_dwarfs) %>% 
  mutate(w_ate = 1 / ifelse(extra_magic_morning == 0, 1 - .fitted, .fitted))
```

## Your Turn 1

_After updating the code chunks below, change `eval = TRUE` before knitting._

Calculate the standardized mean differences with and without weights

```{r, eval = FALSE}
smds <- df %>% 
  mutate(close = as.numeric(close)) %>% 
  tidy_smd(
  .vars = c(wdw_ticket_season, close, weather_wdwhigh),
  .group = extra_magic_morning,
  .wts = w_ate
)
```


Create the Love Plot using ggplot

```{r, eval = FALSE}
ggplot(
  data = smds,
  aes(x = abs(smd), y = variable, group = weights, color = weights)
) +
  geom_line(orientation = "y") +
  geom_point() + 
  geom_vline(xintercept = 0.1, color = "black", size = 0.1)
```



## Your Turn 2

Create an unweighted ECDF for `weather_wdwhigh` by whether or not the day had Extra Magic Hours.

```{r, eval = TRUE}
ggplot(df, aes(x = weather_wdwhigh, color = factor(extra_magic_morning))) +
  geom_ecdf() +
  scale_color_manual("Extra Magic Hours", values = c("#5154B8", "#5DB854"),
                     labels = c("Yes", "No")) + 
  xlab("Historic Temperature") + 
  ylab("Proportion <= x") 
```


Create an weighted ECDF for `weather_wdwhigh` by whether or not the day had Extra Magic Hours.

```{r, eval = TRUE}
ggplot(df, aes(x = weather_wdwhigh, color = factor(extra_magic_morning))) +
  geom_ecdf(aes(weights = w_ate)) + 
  scale_color_manual("Extra Magic Hours", values = c("#5154B8", "#5DB854"),
                     labels = c("Yes", "No")) + 
  xlab("Historic Temperature") + 
  ylab("Proportion <= x") 
```

