---
title: "Outcome Model"
output: html_document
---


```{r}
library(tidyverse)
library(broom)
library(touringplans)
library(rsample)

seven_dwarfs <- seven_dwarfs_train_2018 %>%
  filter(hour == 9)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **exposure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

## Your turn

Create a function called `ipw_fit` that fits the propensity score model from Exercise 03, incorporates the ATE weights calculated in Exercise 04, and fits a weighted outcome model.

```{r, eval = TRUE}
fit_ipw <- function(split, ...) { 
  .df <- analysis(split)
  
  # fit propensity score model
  propensity_model <- glm(
    extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
    data = .df,
    family = binomial()
  )
  # calculate ATE weights
  
  df <- propensity_model %>%
  augment(type.predict = "response", data = .df) %>%
  mutate(w_ate = 1 / ifelse(extra_magic_morning == 0, 1 - .fitted, .fitted))
  
  # fit correctly bootstrapped ipw model 
  lm(avg_spostmin ~ extra_magic_morning, data = df, weights = w_ate) %>% 
    tidy() 
}
```

Bootstrap this result 1000 times.

```{r, eval = TRUE}
ipw_results <- bootstraps(seven_dwarfs, 1000, apparent = TRUE) %>% 
  mutate(results = map(splits, fit_ipw)) 
```


Calculate the confidence interval

```{r, eval = TRUE}
boot_estimate <- int_t(ipw_results, results) %>%
  filter(term == "extra_magic_morning")
```


Stretch goal: Do the same for a model using matching.
