---
title: "Outcome Model"
format: html
---


```{r}
library(tidyverse)
library(broom)
library(touringplans)
library(rsample)
library(propensity)

seven_dwarfs <- seven_dwarfs_train_2018 |>
  filter(hour == 9)
```

We are interested in examining the relationship between whether there were "Extra Magic Hours" in the morning (the **exposure**) and the average wait time for the Seven Dwarfs Mine Train the same day between 9am and 10am (the **outcome**).

## Your turn

_After updating the code chunks below, change `eval = TRUE` before rendering._

Create a function called `ipw_fit` that fits the propensity score model from Exercise 03, incorporates the ATE weights calculated in Exercise 04, and fits a weighted outcome model.

```{r}
#| eval: false
fit_ipw <- function(split, ...) { 
  .df <- analysis(split)
  
  # fit propensity score model
  propensity_model <- glm(
    extra_magic_morning ~ wdw_ticket_season + close + weather_wdwhigh,
    data = .df,
    family = binomial()
  )
  
  # calculate ATE weights
  .df <- propensity_model |>
    augment(type.predict = "response", data = .df) |> 
    mutate(w_ate = wt_ate(.fitted, extra_magic_morning))

  # fit correctly bootstrapped ipw model 
  lm(avg_spostmin ~ extra_magic_morning, data = .df, weights = w_ate) |>
    tidy() 
}
```

Bootstrap this result 1000 times.

```{r}
#| eval: false
set.seed(1234)

ipw_results <- bootstraps(seven_dwarfs, 1000, apparent = TRUE)

ipw_results <- ipw_results |>
  mutate(results = map(splits, fit_ipw)) 
```


Bonus! 

```{r}
ipw_results |>
  mutate(
    estimate = map_dbl(
      results,
      # pull the `estimate` for `extra_magic_morning` for each fit
      \(.fit) .fit |>
        filter(term == "extra_magic_morning") |>
        pull(estimate)
    )
  ) |>
  ggplot(aes(estimate)) +
  geom_histogram(fill = "#D55E00FF", color = "white", alpha = 0.8)

```


Calculate the confidence interval

```{r}
#| eval: false
boot_estimate <- int_t(ipw_results, results) |>
  filter(term == "extra_magic_morning")
```




Stretch goal: Do the same for a model using matching.
